PANCHANGE_data_preprocessing

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
#library(psych)
library(tidyverse)
library(eeptools) #Needed to calculate age from birthdate
```

>>>>

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(psych)
library(tidyverse)
library(eeptools) #Needed to calculate age from birthdate
```
